Title here

### 2016-12-07 portfolio/text/ms.Rmd
Add remaining edits from Eric

Managing natural resources and sustaining the livelihoods of those that depend
on their extraction is difficult. These professions tend to have high
year-to-year variability in income [@mishra2002; @sethi2012b]. In addition to
economic risk, such as changes in demand, individuals dependent on natural
resources are also subject to biological and environmental variability. For
example, drought and flooding are a major source of risk to agricultural food
security and farmers' incomes [@gregory2005], and catastrophic disease outbreaks
and wildfires increase risk for the logging industry [@kirilenko2007].

>>>>

Managing natural resources and sustaining the livelihoods of those that depend
on their extraction is difficult. These professions tend to have high
year-to-year variability in income relative to individuals who don't rely on
natural resources as a source of income  [@mishra2002; @sethi2012b]. In
addition to economic risk, such as changes in demand or prices, individuals
dependent on natural resources are also subject to biological and environmental
variability. For example, drought and flooding are a major source of risk to
agricultural food security and farmers' incomes [@gregory2005], and
catastrophic disease outbreaks and wildfires increase risk for the logging
industry [@kirilenko2007].
